### 2017-06-09 sheets/talk-6/sheet-6.tex
Second part of sample solution 6.10

        Now we define two maps
        \begin{alignat*}{4}
          g_1 &\from Z \to C&  \qquad g_1 &:= i \of f_1 \\
          g_2 &\from Z \to E&         g_2 &:= m \of j \of \bar{f}
        \end{alignat*}
        and show that the diagram
        \[ \xymatrix{
          Z \ar[r]^{g_1} \ar[d]^{g_2} & C \ar[d]^l \\
          E \ar[r]^n & F
        } \]
        commutes and is therefore a pullback square of the right-hand square:
        \begin{alignat*}{2}
          l \of g_1
          &= l \of i \of f_1 \\
          &= l \of i \of h \of \bar{f} \\
          &= n \of m \of j \of \bar{f} \\
          &= n \of g_2
        \end{alignat*}
        Now because the right-hand square is a pullback there is a unique map $\bar{g} \from Z \to B$, such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{g_1}
            \ar@{.>}[dr]|{\bar{g}}
            \ar@/_/[ddr]_{g_2} \\
          & B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
          & E \ar[r]^n & F
        } \]
        commutes.
        By showing that this diagram comutes for $\bar{g} = f_1$ and for $\bar{g} = h \of \bar{f}$ we show $h \of \bar{f} = f_2$.
        \begin{itemize}
          \item[1.]We have $i \of f_1 = g_1$ by definition and $k \of f_1 = m \of f_2 = m \of j \of \bar{f} = g_2$.
          \item[2.]We have $(i \of h) \of \bar{f} = i \of f_2$ and $(k \of h) \of \bar{f} = (m \of j) \of \bar{f}$.
        \end{itemize}

        We have shown that the diagram
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\bar{f}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes for the given $\bar{f}$. We now have to prove that this $\bar{f}$ is unique.
        We assume a map $\tilde{f} \from Z \to A$ such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\tilde{f}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes. But than we have another map such that the diagram for the outer square commutes:
        \[ \xymatrix{
          Z \ar@/^/[drrr]^{i \of f_1}
            \ar@{.>}[dr]|{\tilde{f}}
            \ar@/_/[ddr]_{f_2} & & \\
            & A \ar[r]_h \ar[d]^j & B \ar[r]_{i} & C \ar[d]_l \\
            & D \ar[r]^{m} & E \ar[r]^n & F
        } \]
        We conclude that $\bar{f} = \tilde{f}$.
      \item[``$\Leftarrow$'']
    \end{itemize}
  \end{proof}
\end{answer}

>>>>

        Now we define two maps
        \begin{alignat*}{4}
          g_1 &\from Z \to C&  \qquad g_1 &:= i \of f_1 \\
          g_2 &\from Z \to E&         g_2 &:= m \of j \of \bar{f}
        \end{alignat*}
        and show that the diagram
        \[ \xymatrix{
          Z \ar[r]^{g_1} \ar[d]^{g_2} & C \ar[d]^l \\
          E \ar[r]^n & F
        } \]
        commutes and is therefore a pullback square of the right-hand square:
        \begin{alignat*}{2}
          l \of g_1
          &= l \of i \of f_1 \\
          &= l \of i \of h \of \bar{f} \\
          &= n \of m \of j \of \bar{f} \\
          &= n \of g_2
        \end{alignat*}
        Now because the right-hand square is a pullback there is a unique map $\bar{g} \from Z \to B$, such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{g_1}
            \ar@{.>}[dr]|{\bar{g}}
            \ar@/_/[ddr]_{g_2} \\
          & B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
          & E \ar[r]^n & F
        } \]
        commutes.
        By showing that this diagram comutes for $\bar{g} = f_1$ and for $\bar{g} = h \of \bar{f}$ we show $h \of \bar{f} = f_2$.
        \begin{itemize}
          \item[1.]$\bar{g} = f_1$: We have $i \of f_1 = g_1$ by definition and $k \of f_1 = m \of f_2 = m \of j \of \bar{f} = g_2$.
          \item[2.]$\bar{g} = h \of \bar{f}$: We have $(i \of h) \of \bar{f} = i \of f_2$ and $(k \of h) \of \bar{f} = (m \of j) \of \bar{f}$.
        \end{itemize}

        We have shown that the diagram
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\bar{f}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes for the given $\bar{f}$. We now have to prove that this $\bar{f}$ is unique.
        We assume a map $\tilde{f} \from Z \to A$ such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\tilde{f}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes. But than we have another map such that the diagram for the outer square commutes:
        \[ \xymatrix{
          Z \ar@/^/[drrr]^{i \of f_1}
            \ar@{.>}[dr]|{\tilde{f}}
            \ar@/_/[ddr]_{f_2} & & \\
            & A \ar[r]_h \ar[d]^j & B \ar[r]_{i} & C \ar[d]_l \\
            & D \ar[r]^{m} & E \ar[r]^n & F
        } \]
        We conclude that $\bar{f} = \tilde{f}$.

      \item[``$\Leftarrow$'']
        Let the pullback square
        \[ \xymatrix{
          A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          D \ar[r]^m & E
        } \]
        be the pullback of $\xymatrix{D \ar[r]^m & E & B \ar[l]_k}$.
        Let
        $ \xymatrix{
          D & Z \ar[l]_{f_2} \ar[r]^{f_1} & C
        } $
        be a diagram. We note that
        \[ \xymatrix{
          Z \ar[r]^{f_1} \ar[d]^{f_2} & C \ar[d]^l \\
          E \ar[r]_l & F
        } \]
        is a pullback square of the right-hand square.
        Thus we have a unique map $\bar{f} \from Z \to B$ such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\bar{f}}
            \ar@/_/[ddr]_{f_2} \\
          & B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
          & E \ar[r]^n & F
        } \]
        commutes. Then
        \[ \xymatrix{
          Z \ar[r]^{\bar{f}} \ar[d]^{f_2} & B \ar[d]^k \\
          D \ar[r]^m && E
        } \]
        is a pullback square of the left-hand square.
        Thus we have a unique map $\bar{g} \from Z \to A$ such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{\bar{f}}
            \ar@{.>}[dr]|{\bar{g}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes. We show that this $\bar{g}$ is the unique map such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\bar{g}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^{i \of h} \ar[d]^j & C \ar[d]^l \\
          & D \ar[r]^{n \of m} & F
        } \]
        commutes.
        The diagram comutes:
        \begin{align*}
          i \of h \of \bar{g} = i \of \bar{f} = f_1 \\
          j \of \bar{g} = f_2
        \end{align*}
        Let $\tilde{g}$ be another map such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{f_1}
            \ar@{.>}[dr]|{\tilde{g}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^{i \of h} \ar[d]^j & C \ar[d]^l \\
          & D \ar[r]^{n \of m} & F
        } \]
        commutes. To show $\bar{g} = \tilde{g}$ it is because of the uniqueness enough to show that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{\bar{f}}
            \ar@{.>}[dr]|{\tilde{g}}
            \ar@/_/[ddr]_{f_2} \\
          & A \ar[r]^h \ar[d]^j & B \ar[d]^k \\
          & D \ar[r]^m & E
        } \]
        commutes.
        We already have $j \of \tilde{g} = f_2$ and only have to show $h \of \tilde{g} = \bar{f}$.
        Because of $\bar{f} = h \of \bar{g}$ it suffices to show $h \of \tilde{g} = h \of \bar{g}$.
        The commuting square
        \[ \xymatrix{
          Z \ar[r]^{i \of h \of \tilde{g}} \ar[d]_{m \of j \of \tilde{g}} & C \ar[d]^f \\
          E \ar[r]^n & F
        } \]
        is another pullback square for the right-hand square.
        Thus we have a unique map $\bar{x} \from Z \to B$ such that
        \[ \xymatrix{
          Z \ar@/^/[drr]^{i \of h \of \tilde{g}}
            \ar@{.>}[dr]|{\bar{x}}
            \ar@/_/[ddr]_{m \of j \of \tilde{g}} \\
          & B \ar[r]^i \ar[d]^k & C \ar[d]^l \\
          & E \ar[r]^n & F
        } \]
        commutes.
        We get $h \of \tilde{g} = h \of \bar{g}$ when we show that this diagram commutes for $\bar{x} = h \of \tilde{g}$ and $\bar{x} = h \of \bar{g}$.

        \begin{itemize}
          \item[1.]$\bar{x} = h \of \tilde{g}$:
            We have $i \of h \of \tilde{g} = i \of h \of \tilde{g}$ and $m \of j \of \tilde{g} = k \of h \of \tilde{g}$.
          \item[2.]$\bar{x} = h \of \bar{g}$:
            We have $i \of h \of h = i \of f_1 = i \of h \of \tilde{g}$. Furthermore we have
            \begin{alignat*}{3}
              & &\quad&  m \of j \of \tilde{g} \\
              &=&& m \of f_2 \of \tilde{g} \\
              &=&& m \of j \of \bar{g} \\
              &=&& k \of h \of \bar{g}.
            \end{alignat*}
        \end{itemize}
        Thus $h \of \tilde{g} = h \of \bar{g}$. Hence the outer square is a pullback.\qedhere
    \end{itemize}
  \end{proof}
\end{answer}
